Graph Generators: State of the Art and Open Challenges

### 2019-07-14 generators_community_detection.tex
Added stochastic block models

>>>>

\paragraph{Stochastic Block Models} Another popular famility of generators
widely use in the community detection field are the stochastic block
models~\cite{holland1983stochastic}. In such models, the community structure of
the graph is typically defined as an array of $n$ community or clusters sizes,
and a density square matrix of size $nxn$ containing the density of
intra-cluster edges (in the diagonal of the matrix) and the density of
inter-cluster edges. Then, an stochastic procedure is run to sample graphs
from such array and matrix, using the sizes to compute the possible edges
and the densities as probabilities of such edges to exist. The popularity of
these methods stem from its simplicity and scalability, which makes them
suitable for generating large graphs fast and in a distributed environments,
provided that the density matrix is sparse (as it happens in most of real
                                            world graphs). Moreover, given
that the generation process of such models is mathematically tractable, they
are typically used to analyze the limitations of community detection
algorithms such as those based on modularity
optimization~\cite{fortunato2007resolution} or based on
triads~\cite{prat2016put}. Extensions of such models exist, such as the
Mixed Membership Stochastic Block Model~\cite{arioldi2008mixed}, for
overlapping communities.
